better title eventually

### 2015-05-11 cs261n-paper/paper.tex
more writing

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
It is easy to drastically overestimate user comprehension 
and therefore be misguided for user behavior. 
Even though people download and install things all the time, 
they do not know how to do it securely, and worse, 
they are habituated into doing it a certain way. 
What users had trouble with were the most basic tasks, 
such as downloading and installing Tor, rather than 
nagivating a robust menu or understanding subtleties of security guarentees. 
This is really troubling, and matters for things like Tor. 
We use this insight to fix a bunch of stuff and also 
present a new experiment with a basic enough focus, 
making us the first to focus on censorship too. 
\end{abstract}

\section{Introduction} %this should CLEARLY state the results. 
Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

@@

\subsection{Tor} 
Talk about anything relevant to Tor. Just enough background so
that people who have never heard of it will know what I am talking
about, but no more than that.

\subsection{User behavior}
Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.

\subsection{Usable security impact} 
cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.

@@

\subsection{Censorship} 
Motivational paragraph time about how this is so everywhere.

@@

\section{UX sprint} 
Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
Appendix for additional information.

\subsection{Takeaways} 
highlight what we learned and use this to transition into 
the design of the next experiment.

@@

\subsection{Overview}
For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

@@

\subsection{Censorship Environment Simulation}
For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thusly require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
\item{DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
\item{Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
\end{itemize}

Is there a way to target testing of specific transports?
Is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\subsection{Web Browsing Tasks}
The tasks below are designed to be easy and quick to complete for an average
computer user. This design is critical since the objective of the experiment is to observe
how comfortable users are with circumventing censorship, which we indirectly measure
by taking data regarding how participants complete the task. Giving participants tasks 
they are not comfortable with performing or sending them to websites which they are 
unfamiliar with will introduce more variables into the experiment to account for. 
Specifically, we would need to separate any confusion caused by the task itself versus
the task of circumventing censorship.

@@

\subsection{Methodology}  
We plan to recruit up to 200 users for the purpose of this study, 
making it largest user study to date examining Tor (check this). 
This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley, which consists of 36 laptops with 
cubicle walls separating each laptop. We will use individual host firewalls to simulate
the censorship environments and will write a browser extension to 
log when user activity, such as what websites they were successfully able to visit. 
The total length of the experiment, including briefing, completing the censorship 
circumvention tasks, exit survey, and debriefing, will take less than an hour. 
Participants will be compensated \$30 for their time, 
which is more to cover minimum wage and transportation costs

\subsection{Data}

\subsubsection{Measurements}
Screen capture, timing, completion, clicks, etc. Things to measure
about the activity.

\subsubsection{Feedback} 
Talk about the exit survey and what that covers. 
Explain why we want to know what we are asking about. 
And why this matters.

\section{Discussion} 
Discuss the hypotheses we have here for the experiment.

And any work that needs to be done for the experiment.

>>>>

% is the abstract missing some oomph? 
% I don't know how much the storyline is showing through.. or what we are testing. 
\begin{abstract}
\indent \indent It is easy to drastically overestimate user comprehension 
and therefore be misguided for user behavior. 
Even though people download and install things all the time, 
they do not know how to do it securely, and worse, 
they are habituated into doing it a certain way. 
What users had trouble with were the most basic tasks, 
such as downloading and installing Tor, rather than 
nagivating a robust menu or understanding subtleties of security guarentees. 
This is really troubling, and matters for things like Tor. 
We use this insight to fix a bunch of stuff and also 
present a new experiment with a basic enough focus, 
making us the first to focus on censorship too. 
\end{abstract}

\section{Introduction} %this should CLEARLY state the results. 
\indent \indent Talk about the results and contributions concretely.
As short as possible summary of UX sprint here. %only what is necessary to understand results. 
Talk about the changes resulted in the Tor browser here.
As short as possible summary of lessons learned, 
and also a short as possible motivation for censorship work here. %yep, same.
Talk about the experiment design quickly here.

@@

\subsection{Tor} 
\indent \indent Talk about anything relevant to Tor. Just enough background so
that people who have never heard of it will know what I am talking
about, but no more than that.

\subsection{User behavior}
\indent \indent Then also talk about any of the behaviors we are trying to mitigate,
or talk about the average user and what they know, how they are motivated,
just sketching out the environment in general.

\subsection{Usable security impact} 
\indent \indent cite work which has made a huge impact on how people use it, and 
other things which still remain broken because of usability issues.

@@

\subsection{Censorship} 
\indent \indent Motivational paragraph time about how this is so everywhere.

@@

\section{UX sprint} 
\indent \indent Talk about it just enough that it makes a good storyline for the experiment that we 
are proposing a design of. Motivate it a little bit, and tell a story. Then refer to the 
Appendix for additional information.

\subsection{Impact}
\indent \indent whoo talk about the cool stuff that happened next here. 
This means talking about the tickets and changes made 
to the Tor browser, the start of a user manual, and 
increased Tor UX efforts as a whole.

\subsection{Takeaways} 
\indent \indent highlight what we learned and use this to transition into 
the design of the next experiment.

@@

\subsection{Overview}
\indent \indent For users to circumvent censorship in their resident countries, they will need to configure Tor to set up a proxy, bridge, or both. There is a configuration wizard to help guide users through setting up their connection, but our hypothesis is that the average user will not easily be able to configure Tor correctly in these adverse settings, as they require the user to provide IP addresses of proxies or bridges to use. The goal of our experiment is to see how successful users are at carrying out common browsing tasks in an adversarial setting using Tor.

@@

\subsection{Censorship Environment Simulation}
\indent \indent For our experiment, we plan to simulate and test three distinct censorship environments
which vary in their methods of censorship and thusly require distinct responses from our 
participants to circumvent successfully. These environments are designed with respect to 
common censorship techniques employed 
today along with knowledge of how pluggable transports will need to be used.
For instance, some of Tor's pluggable transports work in censorship environments
where others do not. Additionally, some of them require additional information (like bridge 
addresses) before they enable the user to successfully circumvent censorship. 
Details of the three censorship environments are below, increasing in 
order of censorship comprehensiveness and, therefore, difficulty to circumvent.

@@

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item{\bfseries Corporate network.}
A simulation of an enterprise or educational firewall.
Blocks all services but HTTP, HTTPS, and DNS.
Certain non-work-related domains, like youtube.com and torproject.org,
are blocked by DNS and HTTP inspection.
Blocked requests are redirected to a block page.
%what do users need to do to circumvent this? 
\item{\bfseries DNS-only censor.}
This censor injects false replies to DNS queries
for forbidden domain names (DNS poisoning),
but does not do deep packet inspection on TCP streams.
Unlike the corporate censor, this censor allows protocols
outside a small whitelisted set.
%what do users need to do to circumvent this? 
\item{\bfseries Comprehensive censor.}
Employs a variety of techniques, depending on the target.
May do DNS poisoning, IP blocking, and inspection of TCP streams
(examining the URL of HTTP requests, for example).
Some domains may be blocked by DNS and deep packet inspection;
others may additionally be blocked by IP address.
Tor relays are blocked by IP address.
Some domains, like wikipedia.org, may allow HTTP but not HTTPS.
Blocked requests fail silently (no block page).
%what do users need to do to circumvent this? 
\end{itemize}

We plant to present our work at HotPETS2015 and solicit feedback on the design 
of this experiment. Specifically, we would want a reliable way to target the testing of 
specific transports. But given that the average user would not have domain knowledge of 
what transports are for Tor, is there anything to infer from participants' selection of transports, 
or do we assume they are trying transports at random?

\subsection{Web Browsing Tasks}
\indent \indent The tasks below are designed to be easy and quick to complete for an average
computer user. This design is critical since the objective of the experiment is to observe
how comfortable users are with circumventing censorship, which we indirectly measure
by taking data regarding how participants complete the task. Giving participants tasks 
they are not comfortable with performing or sending them to websites which they are 
unfamiliar with will introduce more variables into the experiment to account for. 
Specifically, we would need to separate any confusion caused by the task itself versus
the task of circumventing censorship.

@@

\section{Methodology}

\indent \indent Talk about the two-pronged qualitative and empirical data measurement stuff here.

\subsection{Qualitative Data} 
Write about the exit survey here. Write down number of questions, surveygizmo, etc.

\subsection{Empirical Data} 
Screen capture, timing, completion, clicks, etc. Things to measure about the activity.

\subsection{Experimental Setup}

\indent \indent We plan to recruit up to 200 users for the purpose of this study, making this the largest user 
study to date examining Tor. We do this in order to increase our chances at recruiting a diverse
user population, ranging in age, gender, technical fluency, and other characteristics. Since Tor 
does not keep information regarding its user base, we will try to obtain a user base representative of
the average Internet using-population. Additionally, recruiting a large number of participants has the 
benefit of ensuring enough samples in order to have significant effect sizes in 
each simulated censorship environment.

This study will be conducted at the Experimental Social Science Laboratory (Xlab)
at the University of California, Berkeley. Recruitment will be conducted through Craigslist. 
Although Xlab provides a portal in which researchers can recruit a pre-registered user base,
we choose to not recruit through this portal, as their participants mostly consist of mostly Berkeley 
students. The laboratory setting consists of 36 Toshiba Tecra R850 laptops with cubicle walls 
separating each laptop. Since we do not have the ability to employ network-level firewalls in this
laboratory setting, we will use individual host firewalls to simulate the censorship environments.  
We will write and employ a browser extension will record user activity, such as how many times they 
clicked, what websites they were successfully able to visit, and how long they took to complete 
each task. This is because WHY? %ask david exactly why--technically. isn't the first hop in the clear?

The total length of the experiment, including briefing, completing the censorship circumvention tasks, 
exit survey, and debriefing, will take less than an hour. Participants will be compensated \$30 in the form
of a check or Visa debit card for their time, which is enough to cover minimum wage during their participation 
and their transportation costs to and from the laboratory.

\section{Discussion}

\subsection{Limitations}
\indent \indent One limitation of our experiment is that participants' behaviors in a laboratory setting may
be different to participants' behaviors in the wild. Studies have shown that participants will act in a way which 
will aim to please researchers, trying to simulate what they believe are the results that we desire. Our participants
may be motivated to complete the task in order to succeed at the experiment. One possible effect is that a user
may have more patience to try to succeed at configuring the Tor Browser correctly during the experiment 
compared to if they were attempting the same task at home.

Another limitation of our experiment is that our participants might not have true interest or motivation in
circumventing censorship. We could instead choose to recruit only users who have actively circumvented
censorship or have an interest in Tor, but that study would also come with its own biases and limitations.
We believed that both are worthwhile endeavors; however, we chose to aim for the general population. 
This is because we would eventually want Tor's configuration dialog to be usable for a wide array of users, 
including non-power users, and other types users who might not yet use Tor.

\section{Future Work}
And any work that needs to be done for the experiment. Give a brief timeline.
